%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Employment}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Accedo} % Organization
    {Toronto, CA} % Location
    {Jan 2018 - Apr 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed tv apps for Roku channels using BrightScript and Roku-XML in a multithreaded environment while collaborating with designers and clients.}
        \item {Implemented new features such as closed captions and analytics after API and design changes from clients, while taking in consideration design patterns.}
        \item {Switched from server-side to client-side ad insertion by implementing the Roku Ad Framework.}
        \item {Handled network errors during video playback while providing good UX.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full-Stack Software Developer} % Job title
    {Open Text} % Organization
    {Waterloo, CA} % Location
    {Jan. 2016 - Jun. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed Python Flask web app to input and display data from a PostgreSQL database.}
        \item {Improved navigation and UI of existing pages on web app with intuitive links and search bars.}
        \item {Refactored the code of a scheduler script that periodically fetches new data from the Blackduck REST API for better readability.}
        \item {Integrated the BlackDuck API with the JIRA API to create tickets whenever issues are detected.}
        \item {Deployed the web app and the scheduler as a Windows service.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
