%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {PresentR - Collective Drawing Board} % Project name
    {} % Role
    {} % Location
    {2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Real-time collaborative drawing board on your browser (MSPaint combined with Google Docs). Build with Javascript for frontend, MongoDB for user registration, and Express for routing, websocket for real-time.}
        \item {See polar-temple-50648.herokuapp.com}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {CompAR - Price Comparison AR tool} % Project name
    {} % Role
    {} % Location
    {2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Web AR tool that helps clients compare store products by displaying a 3D model containing relevant product information. Build using A-Frame in Javascript and runs on the browser on phone or computer.}
        \item {See water-winners.glitch.me}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Animal BUZZ - Alexa Skill} % Project name
    {} % Role
    {} % Location
    {2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Quiz game on Alexa to help children associate animals with the sound they make. Build using NodeJs, AWS lambda, and JSON.}
        \item {Download at www.amazon.com/dp/b078x7n8g2/?ref=chatbottle}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lifelog - Github for Life} % Project name
    {} % Role
    {} % Location
    {2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Chrome extension that allows users to update relevant quotes and websites to their profile on a web-based platform. Build using JavaScript.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {BruiseClues - Injury Detector} % Project name
    {} % Role
    {} % Location
    {2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Mobile app that uses the Google Cloud Vision API to identify injuries in pictures while giving relevant treatment information to users. Built with Expo in React Native and works on both Android and iOS.}
        \item {Download the app through Expo on bruiseclues.com}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {CompAR - Price Comparison AR tool} % Project name
    {} % Role
    {} % Location
    {2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Web AR tool that helps clients compare store products by displaying a 3D model containing relevant product information. Build using A-Frame in Javascript and runs on the browser on phone or computer.}
        \item {See water-winners.glitch.me}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
